---
output: github_document
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = T, fig.path = "man/figures/README-")
```

# robustsubsets

## Overview

An R implementation of robust subset selection as described here.

## Installation

You should install Gurobi and the associated R package gurobi before installing robustsubsets.
Gurobi is available for free under academic license at https://www.gurobi.com/.

To install robustsubsets from GitHub, run the following code.

``` {r, eval = F}
devtools::install_github("ryan-thompson/robustsubsets")
```

## Usage

Robust subset selection is a robust version of the classic best subset selection estimator. Robust 
subsets seeks out the best subset of predictors and observations and performs a least squares fit on 
this subset. The number of predictors used by the estimator is controlled by the parameter k, and the 
observations by the parameter h.

```{r, example, results = "hide"} 
library(robustsubsets)

# Set simulation parameters
set.seed(1)
n <- 100
p <- 10
p0 <- 5
n.c <- 10

# Generate training data with 10% contamination
beta <- c(rep(1, p0), rep(0, p - p0))
X <- matrix(rnorm(n * p), n, p)
e <- rnorm(n, c(rep(10, n.c), rep(0, n - n.c)))
y <- X %*% beta + e

# Fit with k=0,...,10 and h=90,100
fit <- rss(X, y, k = 0:10, h = c(90, 100), mio = F)

# Plot coefficient profiles
plot(fit, type = 'profile')

# Plot cross-validation results
plot(fit, type = 'cv')

# Extract coefficients (corresponding to best parameters from cross-validation)
coef(fit)

# Make predictions (using best parameters from cross-validation)
predict(fit, X)
```

## Documentation

See for [robustsubsets_1.0.0.pdf](robustsubsets_1.0.0.pdf) for documentation.
